Data for ms. 1

### 2017-04-04 ms1/ms1.Rmd
new table

conditions = c("AMI", "ALZH", "ALZHDMTA", "ATRIALFB", "CATARACT", "CHRNKIDN", "COPD", "CHF", "DIABETES", "GLAUCOMA", "HIPFRAC", "ISCHMCHT", "DEPRESSN", "OSTEOPRS", "RA_OA", "STRKETIA", "CNCRBRST", "CNCRCLRC", "CNCRPRST", "CNCRLUNG", "CNCRENDM", "ANEMIA", "ASTHMA", "HYPERL", "HYPERP", "HYPERT", "HYPOTH")

multivariate_formula = paste(c('n_claims ~ age + is_female + ', conditions), collapse=' + ') %>% formula

all_condition_model = function(usage) {
  glm(multivariate_formula, data=usage, family='poisson') %>% tidy()
}
```

@@

```{r analyze_function}
analyze = function(this_year) {
  # bene file is already filtered for plan coverage months and good geographies
  bene = read_tsv(sprintf('../bene_%i.tsv', this_year)) %>%
    filter(age >= 65, hmo_months==0) %>%
    mutate(is_female=sex=='female', is_white=race=='white') %>%
    left_join(regions, by='state')

@@

  pde = read_tsv(sprintf('../pde_%i.tsv', this_year)) %>%
    semi_join(bene, by='bene_id') # keep only PDEs for known beneficiaries

@@

  # then by age group
  # (the input to summarize_by is modified, since we want to group by age *group*,
  # not just by raw age)
  age_group_f = function(x) bounds_group(x, c(65, 75, 85, Inf))
  claims_by_age = summarize_by(
    bene %>% mutate(age_group=age_group_f(age)),
    pde, 'age_group') %>%
    mutate(year=this_year)

@@

  # characteristics by consumption
  cc = read_tsv(sprintf('../cc_%i.tsv', this_year))

  usage = pde %>% count(bene_id) %>% rename(n_claims=n) %>%
    right_join(bene, by='bene_id') %>%
    replace_na(n_claims=0) %>%
    left_join(cc, by='bene_id') %>%
    multicol_sum('n_cc', conditions)

@@

>>>>

conditions = c("AMI", "ALZHDMTA", "ATRIALFB", "CATARACT", "CHRNKIDN", "COPD", "CHF", "DIABETES", "GLAUCOMA", "HIPFRAC", "ISCHMCHT", "DEPRESSN", "OSTEOPRS", "RA_OA", "STRKETIA", "CNCRBRST", "CNCRCLRC", "CNCRPRST", "CNCRLUNG", "CNCRENDM", "ANEMIA", "ASTHMA", "HYPERL", "HYPERP", "HYPERT", "HYPOTH")

multivariate_formula = paste(c('n_claims ~ age_over_65 + is_female + ', conditions), collapse=' + ') %>% formula

all_condition_model = function(usage) {
  usage %>%
    mutate(age_over_65 = age - 65) %>%
    glm(multivariate_formula, data=., family='poisson') %>%
    tidy()
}
```

@@

```{r analyze_function}
analyze = function(this_year) {
  # bene file is already filtered for plan coverage months and good geographies
  bene = read_tsv(sprintf('../bene_%i.tsv', this_year)) %>%
    filter(age >= 65, age < 116, hmo_months==0) %>%
    mutate(is_female=sex=='female', is_white=race=='white') %>%
    left_join(regions, by='state')

@@

  # keep only PDEs for known beneficiaries (semi join)
  # convert all amox/clav to just amox
  pde = read_tsv(sprintf('../pde_%i.tsv', this_year)) %>%
    semi_join(bene, by='bene_id') %>%
    mutate(antibiotic=if_else(antibiotic=='amoxicillin/clavulanate', 'amoxicillin', antibiotic))

@@

  # then by age group
  # (the input to summarize_by is modified, since we want to group by age *group*,
  # not just by raw age)
  age_group_f = function(x) bounds_group(x, c(65, 70, 75, 80, 85, 90, 95, 116))
  claims_by_age = summarize_by(
    bene %>% mutate(age_group=age_group_f(age)),
    pde, 'age_group') %>%
    mutate(year=this_year)

@@

  # characteristics by consumption
  cc = read_tsv(sprintf('../cc_%i.tsv', this_year)) %>%
    select(-ALZH)

  usage = pde %>% count(bene_id) %>% rename(n_claims=n) %>%
    right_join(bene, by='bene_id') %>%
    replace_na(list(n_claims=0)) %>%
    left_join(cc, by='bene_id') %>%
    multicol_sum('n_cc', conditions)

@@

## Table 3 caption: model coefficient p-values

Only $p$-values above (less significant than) $10^{-50}$ are shown. All the remaining values are more significant than the ones shown here.

```{r p_values}
data_by_field('condition_model') %>%
  select(term, year, p.value) %>%
  mutate(adj.p=p.adjust(p.value, method='bonferroni'),
         log10.adj.p=log10(adj.p)) %>%
  filter(adj.p > 10^(-50)) %>%
  arrange(desc(log10.adj.p)) %>%
  kable
```
